Open source landscape ecology tools

### 2020-07-10 paper/paper.Rmd
Adding some comments to manuscript

<!--MH: Short paragraph about scale; *grainchanger* https://doi.org/10.1111/2041-210X.13177 -->

@@

<!-- MH: Work-in-Progress -->
<!-- ISOLATION BY RESISTANCE; DOI: 10.1111/j.0014-3820.2006.tb00500.x -->

@@

<!-- MH: This is work in progress. However, there seems to be a lot of connection to basic connectivity. Maybe include here and/or combine the overall topic with connectivity. -->

<!-- Resistance surface -->
<!-- Commute distances -->
<!-- Least cost path -->

<!-- *graph4lg*  -->
<!-- *gdistance* -->
<!-- *lme4* -->
<!-- *HierDpart* -->
<!-- *PopGenReport* -->
<!-- https://dyerlab.github.io/Landscape-Genetics-Data-Analysis/index.html -->

>>>>

<!--MH: Short paragraph about scale; *grainchanger*; DOI: 10.1111/2041-210X.13177 -->

<!-- MH: landscapetools; DOI: 10.1111/2041-210X.13076 -->

@@

<!-- MH: Work-in-Progress -->
<!-- There seems to be a lot of connection to basic connectivity -->
<!-- ISOLATION BY RESISTANCE; DOI: 10.1111/j.0014-3820.2006.tb00500.x -->
<!-- *graph4lg*  -->
<!-- *gdistance* -->
<!-- *lme4* -->
<!-- *HierDpart* -->
<!-- *PopGenReport* -->
<!-- https://dyerlab.github.io/Landscape-Genetics-Data-Analysis/index.html -->

@@

<!-- MH: NLMR; DOI:  https://doi.org/10.1111/2041-210X.13076 -->
